Sampling Strategies in Decisions from Experience

### 2022-05-27 manuscript.Rmd
Add word count

keywords          : "decisions from experience, information sampling, evidence accumulation, computational modeling, cumulative prospect theory"
wordcount         : ""

>>>>

keywords          : "decisions from experience, information sampling, evidence accumulation, computational modeling, cumulative prospect theory"
wordcount         : "12,450"
